---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  
)
```

# Thermo_readbacks

<!-- badges: start -->
<!-- badges: end -->

A soon-to-be R package supporting Thermo mass spectrometry instrument readback analysis. Thermo orbitrap mass spectrometers record numerous instrument readbacks including:

* Ambient temperature
* Analyzer temperature
* CEPS Peltier temperature
* Fore vacuum pressure
* high vacuum pressure
* ultra high vacuum pressure

### Supported Instruments

* Q-Exactive family instruments
* Exploris family instruments

### Path to log files

#### Q Exactive

`C:\Xcalibur\system\Exactive\log\`

#### Exploris

`C:\ProgramData\Thermo\Exploris\Log`

# Importing log files

```{r include=FALSE}

source("bin/import_log_files.R")
library(scales)

data <- import_log_files("data/QE_HF/")

```


```{r}


ggplot(data %>% filter(time <= as.Date("2020-12-08")),
       aes(x = time)) +
  geom_line(aes(y = ambient_temperature_raw_c, color = "Ambient Temp")) +
  # geom_line(aes(y = analyzer_temperature_sensor_c, color = "Analyzer Temp sensor")) +
  # geom_line(aes(y = ceps_peltier_temperature_sensor_c, color = "CEPS Peltier temp sensor")) +
  scale_color_brewer(palette = "Set1") +
  # expand_limits(y = c(25,30)) +
  labs(title = "Ambient Temperature",
       y = expression('Temp ('~degree*C*')'),
       x = NULL,
       color = NULL) +
  scale_x_datetime(breaks = scales::breaks_pretty(10)) +
  scale_y_continuous(limits = c(0,NA),
                     breaks = breaks_pretty()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(color = FALSE) +
  ggthemes::theme_hc(base_size = 14) 

```

